---
title: "MAX-503 Assignment 1"
output:
  pdf_document: default
  html_notebook: default
---

1. Create a text vector called Months with names of the 12 months of the year.

```{r}
Months<-c("January","February","March","April","May","June","July","August","September",
          "October","November","December")
Months

```

2. Create a numeric vector Summer, with Calendar month index positions for the
summer months (inclusive, with 4 elements in all).
```{r}
Summer<-c(6,7,8,9)
```

3. Use vector indexing to extract the text values of Months, indexed by Summer. 
```{r}
Months[c(Summer)]
```

4. Multiply Summer by 3. What are the values of Months, when indexed by Summer
 multiplied by 3? Why do you get that answer?
```{r}
Months[Summer*3]
```
We get this output because Summer*3 changes the vector summer to (18,21,24,27) and the vector Months has values only till 12. Hence, returning null values.


5. What is the mean(average)summer month, as an integer value? Which value of Months
corresponds to it? Why do you get that answer?
```{r}
Summer_mean<-mean(Summer)
Summer_mean
Months[Summer_mean]
```
The mean of summer returns 7.5 and by default the index rounds the function down to 0 decimal. So RStudio only considers 7 as the index.

6. Use the floor() and ceiling() functions to return the upper and lower limits of Months for
the average Summer month. (Hint: to find out how a function works, use R help if
needed.)
```{r}
Months[floor(Summer_mean)]
Months[ceiling(Summer_mean)]
```

7. Using the store.df data from Week 2 lecture, how many visits did Bert’s store have? 
```{r}
store.num <- factor(c(3, 14, 21, 32, 54))   # store id 
store.rev <- c(543, 654, 345, 678, 234)   # store revenue, $K 
store.visits <- c(45, 78, 32, 56, 34)    # visits, 1000s 
store.manager <- c("Annie", "Bert", "Carla", "Dave", "Ella") 
(store.df <- data.frame(store.num, store.rev, store.visits, store.manager, stringsAsFactors=F))
store.df
summary(store.df)

store.df[2 , 3]
```
Bert's store had 78 visits.

8. It is easy to make mistakes in indexing. How can you confirm that the previous answer is
actually from Bert’s store? Show this with a command that produces
 no more than 1 row of console output.
```{r}
store.df[store.df$store.manager=="Bert","store.visits"]
```
 
 Installing package to convert to PDF
```{r}
tinytex::install_tinytex()
```
 
 